Revisiting Multi-Domain Machine Translation

### 2020-08-27 2020/tacl2020/multidomain.tex
30 cluster table

\begin{table*}[t]
  \centering
  \begin{tabular}{|p{1.3cm}|*{11}{c|}} \hline
   Cluster/ & \multirow{2}{*}{size} &\system{Mixed}&\system{FT}&\system{FT}&\system{MDL}&\system{DC}&\system{DC}&\multirow{2}{*}{\system{TTM}}&\multirow{2}{*}{\system{ADM}}&\multirow{2}{*}{\system{DM}}&\multirow{2}{*}{\system{LDR}}  \\ 
   Model& & \system{-Nat} & \system{Full} & \system{Res} &\system{Res} & \system{-Feat}& \system{-Tag}& & & & \\ \hline
24(med)&8129 / 3(law)&90.4&90.4&90.4&90.4&100.0&65.6&100.0&90.4&100.0&100.0 \\
13(law)&17260 / 52&67.6&75.4&74.3&74.3&75.0&54.7&74.7&75.9&65.9&76.9 \\
28(med)&25561 / 54&71.6&68.7&68.1&70.2&71.0&42.5&72.0&71.3&65.6&72.6 \\
19(IT)&27227 / 88&58.5&63.0&60.9&63.9&63.7&57.2&59.4&61.1&60.5&60.3 \\
0(IT)&27436 / 72&43.9&33.3&45.4&45.4&49.9&15.4&46.8&49.2&46.6&47.8 \\
22(bank)&27534 / 103&91.5&93.7&93.4&93.9&92.5&72.8&92.3&93.2&91.4&93.4 \\
25(med)&28237 / 56&57.0&44.8&48.2&49.1&54.6&47.2&49.8&54.2&45.1&52.4 \\
16(med)&30443 / 18&57.2&70.4&77.4&73.5&61.8&54.2&58.4&58.1&52.5&58.3 \\
23(med)&47065 / 23&24.5&27.2&26.5&28.5&30.5&27.3&32.0&24.4&29.0&29.8 \\
17(med)&54378 / 26&39.9&40.3&41.6&38.0&37.1&36.6&35.2&35.4&31.3&33.7 \\
8(IT)&61353 / 214&46.9&53.1&55.8&53.6&48.9&45.1&48.8&50.9&43.0&46.7 \\
1(med)&68108 / 122&47.2&47.5&48.7&45.1&46.8&39.1&45.4&44.2&40.7&44.9 \\
7(med)&91464 / 30&41.3&35.5&41.4&39.9&41.4&36.5&37.3&37.1&40.7&41.8 \\
11(med)&92982 / 38&31.6&42.6&31.8&35.4&36.0&29.6&36.7&32.7&26.5&36.6 \\
29(law)&109260 / 242&65.9&69.2&67.6&67.7&66.0&63.8&65.1&64.7&62.4&65.9 \\
27(med)&109324 / 49&11.0&9.6&8.7&9.2&10.0&19.4&9.4&7.9&10.7&10.6 \\
5(med)&109949 / 267&46.3&47.4&46.9&45.4&44.0&42.9&43.7&44.3&40.9&45.7 \\
6(med)&133395 / 73&37.2&38.9&38.7&36.8&37.5&27.5&38.0&37.2&31.3&35.9 \\
26(med)&134828 / 428&31.8&30.8&31.8&31.2&31.9&32.6&32.2&30.5&29.6&31.2 \\
15(bank)&136944 / 674&46.5&51.5&47.9&48.0&46.6&46.0&45.8&45.7&42.9&46.0 \\
4(law)&137451 / 1016&77.1&85.3&83.5&83.3&75.8&46.1&74.2&73.3&63.2&75.9 \\
2(med)&182594 / 85&70.6&75.8&71.7&69.4&68.2&67.3&67.3&68.6&65.6&68.2 \\
20(med)&182990 / 71&47.4&47.2&46.8&47.2&48.4&47.5&48.8&47.3&47.1&46.8 \\
21(IT)&222802 / 868&38.7&38.8&39.0&37.2&37.5&35.9&36.9&37.1&33.4&37.0 \\
10(med)&225347 / 115&40.0&42.6&40.0&38.2&39.9&35.8&39.5&39.1&36.3&40.7 \\
18(med)&245000 / 106&57.7&60.3&58.7&58.6&58.4&56.3&57.3&56.1&54.9&55.9 \\
9(med)&301639 / 145&37.2&37.3&36.5&36.1&36.4&37.7&36.4&35.2&34.2&37.0 \\
3(law)&323474 / 680&50.1&52.0&50.8&50.1&49.1&48.3&49.0&48.2&44.4&49.1 \\
14(med)&333957 / 146&31.6&31.4&31.9&33.0&32.5&34.1&31.4&32.1&30.5&31.8 \\
12(med)&356377 / 148&36.3&36.6&35.9&35.9&35.8&37.0&36.4&35.4&34.2&36.3 \\ \hline
  \end{tabular}
  \caption{Detailed results of the experiments with automatic domains}
  \label{tab:automatic_domains}
\end{table*}

>>>>

\begin{table*}[t]
  \centering
  \begin{tabular}{|p{1.3cm}|*{11}{c|}} \hline
   Model/ & \multirow{2}{*}{size} &\system{Mixed}&\system{FT}&\system{FT}&\system{MDL}&\system{DC}&\system{DC}&\multirow{2}{*}{\system{TTM}}&\multirow{2}{*}{\system{ADM}}&\multirow{2}{*}{\system{DM}}&\multirow{2}{*}{\system{LDR}}  \\ 
   Cluster & & \system{-Nat} & \system{Full} & \system{Res} &\system{Res} & \system{-Feat}& \system{-Tag}& & & & \\ \hline
24(med)&8129 / 3(law)&90.4&90.4&90.4&90.4&100.0&65.6&100.0&90.4&100.0&100.0 \\
13(law)&17260 / 52&67.6&75.4&74.3&74.3&75.0&54.7&74.7&75.9&65.9&76.9 \\
28(med)&25561 / 54&71.6&68.7&68.1&70.2&71.0&42.5&72.0&71.3&65.6&72.6 \\
19(IT)&27227 / 88&58.5&63.0&60.9&63.9&63.7&57.2&59.4&61.1&60.5&60.3 \\
0(IT)&27436 / 72&43.9&33.3&45.4&45.4&49.9&15.4&46.8&49.2&46.6&47.8 \\
22(bank)&27534 / 103&91.5&93.7&93.4&93.9&92.5&72.8&92.3&93.2&91.4&93.4 \\
25(med)&28237 / 56&57.0&44.8&48.2&49.1&54.6&47.2&49.8&54.2&45.1&52.4 \\
16(med)&30443 / 18&57.2&70.4&77.4&73.5&61.8&54.2&58.4&58.1&52.5&58.3 \\
23(med)&47065 / 23&24.5&27.2&26.5&28.5&30.5&27.3&32.0&24.4&29.0&29.8 \\
17(med)&54378 / 26&39.9&40.3&41.6&38.0&37.1&36.6&35.2&35.4&31.3&33.7 \\
8(IT)&61353 / 214&46.9&53.1&55.8&53.6&48.9&45.1&48.8&50.9&43.0&46.7 \\
1(med)&68108 / 122&47.2&47.5&48.7&45.1&46.8&39.1&45.4&44.2&40.7&44.9 \\
7(med)&91464 / 30&41.3&35.5&41.4&39.9&41.4&36.5&37.3&37.1&40.7&41.8 \\
11(med)&92982 / 38&31.6&42.6&31.8&35.4&36.0&29.6&36.7&32.7&26.5&36.6 \\
29(law)&109260 / 242&65.9&69.2&67.6&67.7&66.0&63.8&65.1&64.7&62.4&65.9 \\
27(med)&109324 / 49&11.0&9.6&8.7&9.2&10.0&19.4&9.4&7.9&10.7&10.6 \\
5(med)&109949 / 267&46.3&47.4&46.9&45.4&44.0&42.9&43.7&44.3&40.9&45.7 \\
6(med)&133395 / 73&37.2&38.9&38.7&36.8&37.5&27.5&38.0&37.2&31.3&35.9 \\
26(med)&134828 / 428&31.8&30.8&31.8&31.2&31.9&32.6&32.2&30.5&29.6&31.2 \\
15(bank)&136944 / 674&46.5&51.5&47.9&48.0&46.6&46.0&45.8&45.7&42.9&46.0 \\
4(law)&137451 / 1016&77.1&85.3&83.5&83.3&75.8&46.1&74.2&73.3&63.2&75.9 \\
2(med)&182594 / 85&70.6&75.8&71.7&69.4&68.2&67.3&67.3&68.6&65.6&68.2 \\
20(med)&182990 / 71&47.4&47.2&46.8&47.2&48.4&47.5&48.8&47.3&47.1&46.8 \\
21(IT)&222802 / 868&38.7&38.8&39.0&37.2&37.5&35.9&36.9&37.1&33.4&37.0 \\
10(med)&225347 / 115&40.0&42.6&40.0&38.2&39.9&35.8&39.5&39.1&36.3&40.7 \\
18(med)&245000 / 106&57.7&60.3&58.7&58.6&58.4&56.3&57.3&56.1&54.9&55.9 \\
9(med)&301639 / 145&37.2&37.3&36.5&36.1&36.4&37.7&36.4&35.2&34.2&37.0 \\
3(law)&323474 / 680&50.1&52.0&50.8&50.1&49.1&48.3&49.0&48.2&44.4&49.1 \\
14(med)&333957 / 146&31.6&31.4&31.9&33.0&32.5&34.1&31.4&32.1&30.5&31.8 \\
12(med)&356377 / 148&36.3&36.6&35.9&35.9&35.8&37.0&36.4&35.4&34.2&36.3 \\ \hline
  \end{tabular}
  \caption{Detailed results of the experiments with automatic domains}
  \label{tab:automatic_domains}
\end{table*}

\begin{table*}[t]
\centering
  \begin{tabular}{|p{2.3cm}|*{11}{c|}} \hline
   Model/ & \multirow{2}{*}{Averaged size} &\system{Mixed}&\system{FT}&\system{FT}&\system{MDL}&\system{DC}&\system{DC}&\multirow{2}{*}{\system{TTM}}&\multirow{2}{*}{\system{ADM}}&\multirow{2}{*}{\system{DM}}&\multirow{2}{*}{\system{LDR}}  \\ 
   Group cluster & & \system{-Nat} & \system{Full} & \system{Res} &\system{Res} & \system{-Feat}& \system{-Tag}& & & & \\ \hline
10 small&49.5&60.2&60.7&62.6&62.7&63.6&47.3&62.1&61.3&58.8&62.5\\
10 mid&213.7&40.6&42.6&41.9&41.2&40.9&38.3&40.2&39.5&36.9&40.5\\
10 large&338&48.7&50.7&49.5&48.9&48.2&44.6&47.7&47.2&44.4&47.9\\
Avg& &49.8&51.3&51.3&50.9&50.9&43.4&50.0&49.4&46.7&50.29 \\ \hline

  \end{tabular}
   \caption{Average over group of 10 large, medium, small clusters}
  \label{tab:avg_automatic_domains}
\end{table*}
